Box 1 - TDT Curves

### 2023-09-21 ms/ms.qmd
Updted docs. Still need to fix figure diemnsions

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, bayesplot, here, readxl)

@@

##### Evolutionary relationships can help understand thermal tolerance in species lacking thermal tolerance data
The model predicted known data reasonably well for most traits (correlation between known values and values estimated from the model: $z^{TDT}$ – `r cor.test(check_z$trait, check_z$est)$estimate`, 95% CI: `r cor.test(check_z$trait, check_z$est)$conf.int[1]` to `r cor.test(check_z$trait, check_z$est)$conf.int[2]`, p < 0.001; $CT_{max}$ – `r cor.test(check_ctmax$trait, check_ctmax$est)$estimate`, 95% CI: `r cor.test(check_ctmax$trait, check_ctmax$est)$conf.int[1]` to `r cor.test(check_ctmax$trait, check_ctmax$est)$conf.int[2]`, p < 0.001; CFLs – `r cor.test(check_cfls$trait, check_cfls$est)$estimate`, 95% CI: `r cor.test(check_cfls$trait, check_cfls$est)$conf.int[1]` to `r cor.test(check_cfls$trait, check_cfls$est)$conf.int[2]`, p < 0.001), suggesting that even this basic model could be used to provide sensible quantitative measures for *Drosophila* species without heat tolerance estimates. While modelling approaches such as these are not a replacement for actual empirical data, they could be used to provide informed judgements on thermal tolerance in the absence of such information, but should be tested (using cross-validation) and refined when necessary.

@@

```{r, fig-treesub}
#| label: fig-treesub
#| fig-cap: Species included in the dataset and their phylogenetic relationships.

@@

layout(mat = layout.matrix) 
# Plot 1
plot(t, type = "tidy", cex = 0.65)

# Plot 2
plot(check_z$trait ~ check_z$est, ylab = "TDT Slope (z)", xlab = "Estimated TDT Slope", pch = 16, cex = 3, cex.lab = 2)
abline(a = 0, b = 1, col = "red")

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, bayesplot, here, readxl, magick)

@@

##### Evolutionary relationships can help understand thermal tolerance in species lacking data
The model predicted known data reasonably well for most traits (correlation between known values and values estimated from the model: $z^{TDT}$ – `r cor.test(check_z$trait, check_z$est)$estimate`, 95% CI: `r cor.test(check_z$trait, check_z$est)$conf.int[1]` to `r cor.test(check_z$trait, check_z$est)$conf.int[2]`, p < 0.001; $CT_{max}$ – `r cor.test(check_ctmax$trait, check_ctmax$est)$estimate`, 95% CI: `r cor.test(check_ctmax$trait, check_ctmax$est)$conf.int[1]` to `r cor.test(check_ctmax$trait, check_ctmax$est)$conf.int[2]`, p < 0.001; CFLs – `r cor.test(check_cfls$trait, check_cfls$est)$estimate`, 95% CI: `r cor.test(check_cfls$trait, check_cfls$est)$conf.int[1]` to `r cor.test(check_cfls$trait, check_cfls$est)$conf.int[2]`, p < 0.001), suggesting that even this basic model could be used to provide sensible quantitative measures for *Drosophila* species without heat tolerance estimates. While modelling approaches such as these are not a replacement for actual empirical data, they could be used to provide informed judgements on thermal tolerance in the absence of such information, but should be tested (using cross-validation) and refined when necessary.

@@

```{r, fig-treesub}
#| label: fig-treesub
#| fig-cap: Species included in the dataset and their phylogenetic relationships.
#| echo: false
#| message: false

@@

rerun = FALSE
if(rerun){
  pdf(height = 10.2, width = 8.1, file = here::here("output", "fig", "fig1.pdf"))
  layout(mat = layout.matrix) 
  # Plot 1
  plot(t, type = "tidy", cex = 0.65)

  # Plot 2
  plot(check_z$trait ~ check_z$est, ylab = "TDT Slope (z)", xlab = "Estimated TDT Slope", pch = 16, cex = 3, cex.lab = 1.4)
  abline(a = 0, b = 1, col = "red")
  dev.off()
} else {
  fig <- magick::image_read(here::here("output", "fig", "fig1.pdf"))
  plot(fig)
}
```
